Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-01-13 manuscript/suppMat.Rmd
updated simulations

```{r caching, include=FALSE}
library("methods")
library("knitr")
basename <- "manuscript"
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
opts_chunk$set(cache = 2)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
               comment = NA, verbose = TRUE, echo=FALSE)

@@

```{r figure_S2, dependson="plot-options", fig.cap="Posterior means (vertical ticks), 75% credible intervals (heavy lines), and 95% credible intervals (light lines) of climate effects on growth at both levels of inferences. The dashed vertical line is at 0, indicating no effect.", fig.width=8, fig.height=7, cache=FALSE, results='hide'}
gQC <- read.csv("../montana/quadBM/vitalRateRegressions/growth/growthQuants.csv")
gQC <- gQC[129:144,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
gQC$X <- rep(coefNames, each=4)
gQC$rate <- "growth"
sQC <- read.csv("../montana/quadBM/vitalRateRegressions/survival/survivalQuants.csv")
sQC <- sQC[33:48,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
sQC$X <- rep(coefNames, each=4)
sQC$rate <- "survival"
rQC <- read.csv("../montana/quadBM/vitalRateRegressions/colonization/colonizationQuants.csv")
rQC <- rQC[29:44,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
rQC$X <- rep(coefNames, each=4)
rQC$rate <- "colonization"
plotQC <- rbind(gQC,sQC,rQC)
gQ <- ggplot(plotQC, aes(x=species, y=X50., color=rate))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  geom_errorbar(aes(ymin=X2.5., ymax=X97.5.), width=0, position=position_dodge(width=0.5))+
  geom_errorbar(aes(ymin=X25., ymax=X75.), width=0, size=1.25, position=position_dodge(width=0.5))+
  geom_point(size=4, position=position_dodge(width=0.5), shape="|")+
  ylab("Standardized Coefficient Value")+
  xlab("Species")+
  facet_grid(X~.)+
  coord_flip()+
  theme_bw()+
  scale_color_manual(values=c("grey25", "steelblue", "slateblue"))+
  guides(color=guide_legend(title=""))+
  theme(legend.position="top")+
  ggtitle("Quadrat level")

>>>>

```{r caching, include=FALSE}
library("methods")
library("knitr")
library(ggplot2)
library(reshape2)
library(plyr)
library(gridExtra)
basename <- "manuscript"
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
opts_chunk$set(cache = 2)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
               comment = NA, verbose = TRUE, echo=FALSE)

@@

```{r figure_S2, dependson="plot-options", fig.cap="Posterior means (vertical ticks), 75% credible intervals (heavy lines), and 95% credible intervals (light lines) of climate effects on growth at both levels of inferences. The dashed vertical line is at 0, indicating no effect.", fig.width=8, fig.height=7, cache=FALSE, results='hide'}
gQC <- read.csv("../montana/quadBM/vitalRateRegressions/growth/growthQuants.csv")
gQC <- gQC[137:152,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
gQC$X <- rep(coefNames, each=4)
gQC$rate <- "growth"
sQC <- read.csv("../montana/quadBM/vitalRateRegressions/survival/survivalQuants.csv")
sQC <- sQC[33:48,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
sQC$X <- rep(coefNames, each=4)
sQC$rate <- "survival"
rQC <- read.csv("../montana/quadBM/vitalRateRegressions/colonization/colonizationQuants.csv")
rQC <- rQC[29:44,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
rQC$X <- rep(coefNames, each=4)
rQC$rate <- "colonization"
plotQC <- rbind(gQC,sQC,rQC)
gQ <- ggplot(plotQC, aes(x=species, y=X50., color=rate))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  geom_errorbar(aes(ymin=X2.5., ymax=X97.5.), width=0, position=position_dodge(width=0.5))+
  geom_errorbar(aes(ymin=X25., ymax=X75.), width=0, size=1.25, position=position_dodge(width=0.5))+
  geom_point(size=4, position=position_dodge(width=0.5), shape="|")+
  ylab("Standardized Coefficient Value")+
  xlab("Species")+
  facet_grid(X~.)+
  coord_flip()+
  theme_bw()+
  scale_color_manual(values=c("grey25", "steelblue", "slateblue"))+
  guides(color=guide_legend(title=""))+
  theme(legend.position="top")+
  ggtitle("Quadrat level")
